Repeatability of Pre-Flashover Fire Patterns on Gypsum Wallboard

### 2015-04-09 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Need more research on trim command.

>>>>

\begin{figure}[p]
	\centering
	\includegraphics[trim=1.0in, 0.2in, 1.0in, 0.0in, clip=true]{../Figures/IWGB_NG_0_15m}
	\includegraphics[trim=1.0in, 0.2in, 1.0in, 0.0in, clip=true]{../Figures/IWGB_NG_0m} \\	
	\caption[Photographs of the fire effects on the instrumented gypsum wallboard exposed to the natural gas burner fires]{Photographs of the fire effects on the instrumented gypsum wallboard exposed to the natural gas burner fires. For the image on the left, the burner was positioned 0.15~m from the wall.  For the image on the right, the burner was positioned 0.0~m from the wall.}
	\label{IWGB_NG_patterns}
\end{figure}
